\documentclass[10pt,letterpaper,sans]{moderncv}

\usepackage{natbib}
\usepackage{bibentry,xr}
\usepackage[left=0.25in, right=0.375in, top=0.375in, bottom=0.5in]{geometry}

\usepackage{lastpage}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{libertine}
\usepackage[symbol]{footmisc}
\moderncvstyle{classic}
\moderncvcolor{blue}
\providecommand{\NOOP}[1]{}
\setlength{\hintscolumnwidth}{0.08\textwidth}

\newcounter{gitref}
\renewcommand{\thegitref}{[\alph{gitref}]}
\newcommand{\gitcount}{ \refstepcounter{gitref} \thegitref}

	
\linespread{0.95}

\pagestyle{fancy}
\rfoot{\thepage\ of \pageref{LastPage}}

%DOI link
\newcommand*{\doi}[1]{\href{http://dx.doi.org/#1}{doi: #1}}


%Multicolumn
\usepackage{multicol}
%\setlength{\hintscolumnwidth}{2cm}
%\setlength{\separatorcolumnwidth}{1em}

%% Relevant lengths
%\setlength{\hintscolumnwidth}{0.175\textwidth}
%\setlength{\separatorcolumnwidth}{0.025\textwidth}
%\setlength{\maincolumnwidth}{\textwidth-\leftskip-\rightskip-\separatorcolumnwidth-\hintscolumnwidth}
%
%% Definition
%\renewcommand*{\cvitem}[3][.25em]{%
%  \begin{tabular}{@{}p{\hintscolumnwidth}@{\hspace{\separatorcolumnwidth}}p{\maincolumnwidth}@{}}%
%    \raggedleft\hintstyle{#2} &{#3}%
%  \end{tabular}%
%  \par\addvspace{#1}}





\renewcommand*{\cvitem}[3][6pt]{%
	\begin{tabular}{@{}p{\hintscolumnwidth}@{\hspace{\separatorcolumnwidth}}p{\maincolumnwidth}@{}}%
		\raggedleft\hintstyle{#2} &{#3}%
	\end{tabular}%
	\par\addvspace{#1}}

\renewcommand*{\cventry}[7][0pt]{%
	\cvitem[#1]{#2}{%
		{\bfseries#3}%
		\ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}%
		\ifthenelse{\equal{#5}{}}{}{, #5}%
		\ifthenelse{\equal{#6}{}}{}{, #6}%
		\strut%
		\ifx&#7&%
		\else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

\renewcommand*{\cvitemwithcomment}[4][0pt]{%
	\savebox{\cvitemwithcommentbox}{{#3}}%
	\setlength{\cvitemwithcommentskilllength}{\widthof{\usebox{\cvitemwithcommentbox}}}%
	\setlength{\cvitemwithcommentcommentlength}{\maincolumnwidth-\separatorcolumnwidth-\cvitemwithcommentskilllength}%
	\cvitem[#1]{#2}{%
		\begin{minipage}[t]{\cvitemwithcommentskilllength}\usebox{\cvitemwithcommentbox}\end{minipage}%
		\hfill% fill of \separatorcolumnwidth
		\begin{minipage}[t]{\cvitemwithcommentcommentlength}\raggedleft\small\itshape#4\end{minipage}}}

\renewcommand*{\cvlistitem}[2][6pt]{%
	\cvitem[#1]{}{\listitemsymbol\begin{minipage}[t]{\listitemcolumnwidth}#2\end{minipage}}}


\renewcommand*{\namefont}{\fontsize{26}{32}\mdseries\upshape}


\makeatletter
\@ifpackageloaded{moderncvstyleclassic}{%
	\let\oldsection\section%
	\renewcommand{\section}[1]{\leavevmode\unskip\vspace*{-\baselineskip}\oldsection{#1}}%
}{%
}
\makeatother

\newcounter{refcounter}
\newcommand{\refno}[1]{\refstepcounter{refcounter} [\therefcounter]\label{#1}}
%\newcommand{\refno}[1]{}

%CONTACT
%\firstname{Nicholas}
%\familyname{Fournier, PhD}
\name{Nicholas}{Fournier, PhD}
%\address{University of California, Berkeley}{}{}
%\mobile{774-236-0293} % Phone number
\email{nick.fournier@berkeley.edu} % Email ID
\social[github][https://github.com/nick-fournier]{github.com/nick-fournier/}
\social[linkedin][www.linkedin.com/in/nicholas-fournier/]{www.linkedin.com/in/nicholas-fournier/}


\usepackage{etoolbox}

\patchcmd{\makecvhead}{{minipage}[b]}{{minipage}[t]}{}{}

\newsavebox{\mytempbox}
\newlength{\mytitleoffset}
\savebox{\mytempbox}{\addressfont S}
\setlength{\mytitleoffset}{\ht\mytempbox}

\patchcmd{\makecvhead}{\raggedleft\fi}{\raggedleft\fi\vspace{-\mytitleoffset}}{}{}
\patchcmd{\makecvhead}{{tabular}[b]}{{tabular}[t]}{}{}



\begin{document}
	\nobibliography{../mybib}
	\bibliographystyle{plainnat_abbrev.bst}
	
   	\makecvtitle
   	   	
%	\footnotetext{* Numbered and lettered citations refer to relevant publications and GitHub repositories.}

	\vspace{-32pt}   	
	
	
%   	\section{OBJECTIVE}
%   	Accomplished researcher seeking to leverage my advanced statistical and analytical skills into a data science career. My hybrid background in engineering (transportation) and social science (urban planning) allows me to move easily between quantitative and qualitative perspectives. I am passionate about learning how human and engineered systems intersect throughout society and how they might be improved.
   	

   	\subsection{RESEARCH EXPERIENCE -- SELECT PROJECTS}
   	\cventry[1pt]{2020-~~~~~~}{University of California Berkeley}{Postdoctoral Scholar\hrule}{}{}{}
   	\cvitem[-14pt]{}{}

  	\cvlistitem{\textit{\bfseries Exploring the operational and equity benefits of a pre-pay dynamic tolling system [lead researcher]:} \textit{R}-based analytical simulation exploring optimal revenue and traffic flow in dynamic toll price ``futures'' market to enhance price-demand elasticity. Utilized Kernel Density Estimation to smooth traffic flow data for forecasting and pricing models. Funded by California State SB1.}
   	
  	\cvlistitem{\textit{\bfseries Bicycle network connectivity evaluation methodology [lead researcher]:} Bicycle network connectivity performance measure using graph theory and user preference criteria (e.g., route choice models). Intended deployment as Python tool for GIS. Funded by Caltrans.}
  		
	\cvlistitem{\textit{\bfseries Erroneous High Occupancy Vehicle (HOV) Degradation:} Python program to detect operational but mislabeled traffic sensors using machine learning (e.g., k-Nearest Neighbor, Logistic Regression, Random Forest, Support Vector Machines, Local Outlier Factor, Isolation Forest, and Robust Covariance Anomaly Detection). Funded by Caltrans.}
	
  	\cvlistitem{\textit{\bfseries Bicycle level of service measures for the CA State Highway System:} UX research/human factors study to determine bicycle infrastructure preferences using virtual reality bicycle simulator. Estimated using a Latent Class Choice Model capable of accounting for user heterogeneity. Results to align with ``Complete Cities'' project. Funded by Caltrans.}
   	
%  	\cvlistitem{\textit{\bfseries Improved Analysis Methodologies and Strategies for Complete Streets:} Developed \textit{R}-based package for estimating Bicycle Level of Service using the Highway Capacity Manual's methodology with proposed improvements [\ref{bikepave}].}
  	  	   	
   	\cventry[1pt]{2019-2020}{Monash University, Melbourne, Australia}{Research Fellow\hrule}{}{}{}
   	\cvitem[-14pt]{}{}
   	\cvlistitem{\textit{\bfseries Public Transport Research Group:} Advised team of 19 doctoral students conducting industry partnered research in public transportation engineering, planning, policy analysis, and economics.}
   	
   	\cventry[1pt]{2014-2018}{University of Massachusetts Amherst}{Graduate Research Assistant\hrule}{}{}{}
   	\cvitem[-14pt]{}{}
   	\cvlistitem{\textit{\bfseries Sustainable Travel Incentives with Prediction, Optimization and Personalization:} Data fusion population synthesizer using novel combinatorial optimization algorithm in \textit{R} and C++ (demographics, OD-matrices, household/vehicle association, etc.). Mixed-methods include Bayesian Networks, Markov chain Monte Carlo simulation, iterative fitting (matrix raking), robust regression, LASSO/Ridge regularization, and gradient descent. Used as input in larger agent-based discrete choice and simulation to lower energy consumption with user incentives. Joint MIT project sponsored by ARPA-energy.}
   		
%	\cvitem[-14pt]{}{}
%	\cvlistitem{\textit{\bfseries Infrastructure Strategies for Safer Cycling: An evaluation of driver behavior using a driving simulator:} USDOT sponsored UX research project using driving simulator to evaluate bicycle infrastructure based on driver behavior. Analyzed results using statistical inference techniques like ANOVA and interaction models in \textit{R} [\ref{bikesim},\ref{bikesine},\ref{bikeinfra}].}
	
% 	\pagebreak	
	\subsection{ADDITIONAL WORK EXPERIENCE}
	\cventry{2015--2017}{Volpe Transportation Center (U.S. DOT)}{Community Planner (Pathways Intern)}{Cambridge, MA}{}{}	
	\cventry{2013--2014}{Sandis Civil Engineers, Planners, Surveyors}{Design Engineer}{Oakland, CA}{}{}
	\cventry{2011--2013}{Benjamini and Associates, Inc.}{Assistant Engineer}{San Francisco, CA}{}{}

% 	\pagebreak	
	
%	\vspace{-6pt} 	
	\begin{multicols}{2}
	\subsection{EDUCATION}
   	\cventry{}{University of Massachusetts, Amherst}{}{}{}{}
   	\cvitemwithcomment[0pt]{2019}{PhD Civil Engineering -- Transportation, \itshape GPA: 4.0}{}
	\cvitemwithcomment[0pt]{2018}{MS Civil Engineering -- Transportation}{}
	\cvitemwithcomment[0pt]{2017}{Master of Regional Planning}{}
   	\cvitemwithcomment[0pt]{2011}{BS Civil \& Environmental Engineering}{}
   	\cvitemwithcomment[0pt]{}{\itshape Dissertation: Equity and efficiency in multi-modal transportation systems}{}

   	\vfill\null
   	\columnbreak

   	\subsection{AWARDS}
   	\cvitemwithcomment{~}{}{}
	\cvitemwithcomment{2018}{Eno Fellow -- Eno Future Leadership Conference}{}
	\cvitemwithcomment{2015-2018}{Dwight D. Eisenhower Transportation Fellowship}{}
	\cvitemwithcomment{2016-2017}{Outstanding Student of the Year}{}
	\cvitemwithcomment{2015}{Daniel B. Fambro Student Paper Award -- ITE}{}
	\end{multicols}
	
	\vspace{-12pt}

{	\small
	\subsection{SELECT PUBLICATIONS}
	\cvitem{2021\refno{pedtransit}}{\hspace{0cm}\bibentry{Fournier2021pedtransit}.}
	\cvitem{\refno{optequity}}{\hspace{0cm}\bibentry{Fournier2021optequity}.}
%	\cvitem{\refno{bikepave}}{\hspace{0cm}\bibentry{Huang2021}.}
	\cvitem{2020\refno{vot}}{\hspace{0cm}\bibentry{Fournier2020vot}}
	\cvitem{\refno{popsynth}}{\hspace{0cm}\bibentry{Fournier2020workpop}}
	\cvitem{\refno{bikesim}}{\hspace{0cm}\bibentry{Fournier2020bikesim}}
%	\cvitem{\refno{astonlanduse}}{\hspace{0cm}\bibentry{Aston2020}}
%	\cvitem{\refno{curriedrt}}{\hspace{0cm}\bibentry{Currie2020}}
	\cvitem{2017\refno{bikesine}}{\hspace{0cm}\bibentry{Fournier2017sine}}
%	\cvitem{\refno{bikeinfra}}{\hspace{0cm}\bibentry{Fournier2017mixed}}
}
	
	
	
% 	\section{LEADERSHIP \& ACTIVITIES}
% 	\cvlistitem[0pt]{Co-host of Eureka! Externships, Girls Inc., Holyoke, MA}
% 	\cvlistitem[0pt]{Faculty hiring committee member}
% 	\cvlistitem[0pt]{UMass Summer Transportation Institute presenter and host}
% 	\cvlistitem[0pt]{Planning Student Organization Treasurer}
% 	\cvlistitem[0pt]{New England Institute of Transportation Engineers Student Member}
% 	\cvlistitem[0pt]{American Planning Association Student Member}
% 	\cvlistitem[0pt]{San Francisco Bicycle Coalition, MassBike, League of American Bicyclists}

\end{document}
